Formalizing Stack Safety as a Security Property

### 2021-07-08 submission3/main.tex
starting on 8

To this point we have ignored function arguments, since our simplest model places them in
registers. We now show how to implement two kinds of protected
sharing: passing by value on the stack, and passing by reference. We first explore
some examples and then move on to
extending our formalization.

@@

Our model provides only limited support for handling fully first-class pointers into
stack frames, e.g., pointers obtained by taking the address of a local variable.
Unlike pass-by-reference, there is no easy way to model the intended
sharing behavior of such pointers in terms of stack frame activation patterns.
The best approximation we can make is to treat an address-taken variable in the
same way as a passed argument, with the additional property
that it remains accessible at \emph{all} stack depths above the caller.
This prevents most violations of temporal safety, although stale pointers
can still be used in certain corner cases.
More seriously, callees are permitted to access the location without having
been explicitly given a pointer to it.  Preventing the latter kind of abuse
is the provence of a fine-grained memory safety policy, e.g., based on
capabilities
(implemented by tags or otherwise); we would argue it is beyond the scope of
stack safety \emph{per se}.

>>>>

To this point we have ignored function arguments, by assuming that they are placed
in registers (which are implicitly shared by all functions). 
We now show how to implement two kinds of protected
sharing of stack contents: passing by value on the stack, and passing by reference. We first explore
some examples and then extend our formalization.

@@

Our approach provides only limited support for handling fully first-class pointers into
stack frames, e.g., pointers obtained by taking the address of a local variable.
Unlike with pass-by-reference, there is no easy way to model the intended
sharing behavior of such pointers in terms of stack frame activation patterns.
The best approximation we can make is to treat an address-taken variable in the
same way as a passed argument, with the additional property
that it remains accessible at \emph{all} stack depths above the caller.
This prevents most violations of temporal safety, although stale pointers
can still be used in certain corner cases.
More seriously, callees are permitted to access the location without having
been explicitly given a pointer to it.  Preventing the latter kind of abuse
is the provence of a fine-grained memory safety policy, e.g., based on
capabilities
(implemented by tags or otherwise); we would argue it is beyond the scope of
stack safety \emph{per se}.\apt{Could try to incorporate some of 
  our response to OOPSLA reviewer 1 about this, but I don't see an easy way.}
